---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  # collapse = TRUE,
  results = "asis",
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(ipa)
```

# ipa

<!-- badges: start -->
[![License: MIT](https://img.shields.io/badge/license-MIT-blueviolet.svg)](https://opensource.org/licenses/MIT)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

Convert character vectors between [IPA](https://en.wikipedia.org/wiki/International_Phonetic_Alphabet) and [X-SAMPA](https://en.wikipedia.org/wiki/X-SAMPA) phonetic representations.

## Installation

You can install the development version of **ipa** from GitHub with:

``` r
install_github("rossellhayes/ipa")
```

## Usage

`r sampa("aI pi: \"eI")`

```{r eval = FALSE}
sampa("/aI pi: \"eI/")
```

`r sampa("/aI pi: \"eI/")`

```{r eval = FALSE}
sampa(c("/\"nom.b4e/", "/nO~bR/"))
```

`r sampa(c("/\"nom.b4e/", "/nO~bR/"))`

```{r eval = FALSE}
ipa("/aɪ piː ˈeɪ/")
```

`/aI pi: "eI/`

```{r eval = FALSE}
ipa(c("/ˈnom.bɾe/", "/nɔ̃bʁ/"))
```

`/nom.b4e/`, `/nO~bR/`

<!-- `ipa()` does not work in Rmarkdown, but does work in the console -->

---

Please note that **ipa** is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
